%basic cover letter template
\documentclass{letter}
\usepackage{amssymb,amsmath}
\usepackage{graphicx}

\oddsidemargin=.2in
\evensidemargin=.2in
\textwidth=5.9in
\topmargin=-.5in
\textheight=9in

%\address{Mathematics Department\\University of Illinois\\
%1409 W. Green St\\Urbana, Illinois 61801}

\newcommand {\qed}{\mbox{$\Box$}}
\renewcommand {\iff}{\Longleftrightarrow}
\newcommand {\R}{\mathbb{R}}
\newcommand {\N}{\mathbb{N}}
\newcommand {\Q}{\mathbb{Q}}
\newcommand {\Z}{\mathbb{Z}}

\newcommand {\sub}{\mbox{SB}}


\begin{document}
\begin{letter}{Dr. Janet Kelso \\
Dept. of Evolutionary Genetics \\
Max Planck Institute \\
Leipzig, Germany}


\opening{Dear Dr.Kelso,}

    Please find attached with this letter a manuscript that we are submitting
for possible publication in Bioinformatics.  This paper (Title: DNAism:
Exploring genomic datasets on the web with Horizon Charts) describes a novel
approach to visualize and explore large DNA sequence-based datasets.

Horizon Charts are a powerful visualization technique to explore high density
datasets without losing graphical perception. They have been successfully
applied in the context of time-series data and we think the genomics community
will greatly benefit from them. That is why we have modified an existing
javascript library that captures this method to make it work with genomic
datasets. We call this new library DNAism. We are confident that many
researchers working on genomic data will find our library useful as they will,
among other things, be able to spot common patterns and abnormal behavior
across multiple datasets. In addition, thanks to its clean and effective
interface, researchers will be able, if necessary, to extend the library to
accommodate the peculiarities of their own particular datasets.

Thank you for your efforts in evaluating this submission.  We look forward to
hearing the result of your review process.



\closing{Sincerely,}

David Rio Deiros
\end{letter}

\end{document}

